Supporting Information : Extreme climatic events with asymmetric tail-dependence affect population-extinction risk

### 2019-08-23 SuppMat.Rmd
bug fixed and code modified

    hassell_extrisk_d0$risk_xleft_d0[i]<-ss$risk_xleft[1]
    hassell_extrisk_d0$risk_xright_d0[i]<-ss$risk_xright[1]
}

@@

    msmith_extrisk_d0$risk_xleft_d0[i]<-ss$risk_xleft[1]
    msmith_extrisk_d0$risk_xright_d0[i]<-ss$risk_xright[1]
}

@@

    pennycuick_extrisk_d0$risk_xleft_d0[i]<-ss$risk_xleft[1]
    pennycuick_extrisk_d0$risk_xright_d0[i]<-ss$risk_xright[1]
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_xleft","risk_xright","risk_mleft","risk_mright")
dimnames(res_pennycuick_local)<-list(NULL,cnm,anm)

@@

    verhulst_extrisk_d0$risk_xleft_d0[i]<-ss$risk_xleft[1]
    verhulst_extrisk_d0$risk_xright_d0[i]<-ss$risk_xright[1]
}

@@

  abrewer_extrisk_d0$risk_xleft_d0[i]<-ss$risk_xleft[1]
  abrewer_extrisk_d0$risk_xright_d0[i]<-ss$risk_xright[1]
}

@@

if(noisetype=="extreme"){
  risk_left<-Af$risk_xleft
  risk_right<-Af$risk_xright
}

if(noisetype=="moderate"){
  risk_left<-Af$risk_mleft
  risk_right<-Af$risk_mright
}

plot(Af$d,risk_left,xlim=range(Af$d),ylim=c(0,1),type="b",col="red",
     xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
lines(Af$d,risk_right,type="b",col="blue")

@@

plot(Al$d,risk_left,xlim=range(Al$d),ylim=c(0,1),type="b",col="red",
     xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
lines(Al$d,risk_right,type="b",col="blue")
mtext(paste0("r = ", round(rlist[lasta],5)))

@@

pdf("./Results/allmodel_ext_risk_local_disp_extremenoise.pdf",height=12,width=9)

@@

>>>>

    hassell_extrisk_d0$risk_xleft_d0[i]<-ss$risk_xleft[1]
    hassell_extrisk_d0$risk_xright_d0[i]<-ss$risk_xright[1]

    hassell_extrisk_d0$risk_mleft_d0[i]<-ss$risk_mleft[1]
    hassell_extrisk_d0$risk_mright_d0[i]<-ss$risk_mright[1]
}

@@

    msmith_extrisk_d0$risk_xleft_d0[i]<-ss$risk_xleft[1]
    msmith_extrisk_d0$risk_xright_d0[i]<-ss$risk_xright[1]

    msmith_extrisk_d0$risk_mleft_d0[i]<-ss$risk_mleft[1]
    msmith_extrisk_d0$risk_mright_d0[i]<-ss$risk_mright[1]
}

@@

    pennycuick_extrisk_d0$risk_xleft_d0[i]<-ss$risk_xleft[1]
    pennycuick_extrisk_d0$risk_xright_d0[i]<-ss$risk_xright[1]

    pennycuick_extrisk_d0$risk_mleft_d0[i]<-ss$risk_mleft[1]
    pennycuick_extrisk_d0$risk_mright_d0[i]<-ss$risk_mright[1]
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_xleft","risk_xright","risk_mleft","risk_mright")
dimnames(res_pennycuick_local)<-list(NULL,cnm,anm)

@@

    verhulst_extrisk_d0$risk_xleft_d0[i]<-ss$risk_xleft[1]
    verhulst_extrisk_d0$risk_xright_d0[i]<-ss$risk_xright[1]

    verhulst_extrisk_d0$risk_mleft_d0[i]<-ss$risk_mleft[1]
    verhulst_extrisk_d0$risk_mright_d0[i]<-ss$risk_mright[1]
}

@@

  abrewer_extrisk_d0$risk_xleft_d0[i]<-ss$risk_xleft[1]
  abrewer_extrisk_d0$risk_xright_d0[i]<-ss$risk_xright[1]

  abrewer_extrisk_d0$risk_mleft_d0[i]<-ss$risk_mleft[1]
  abrewer_extrisk_d0$risk_mright_d0[i]<-ss$risk_mright[1]
}

@@

if(noisetype=="extreme"){
  risk_left1<-Af$risk_xleft
  risk_right1<-Af$risk_xright

  risk_left2<-Al$risk_xleft
  risk_right2<-Al$risk_xright
}

if(noisetype=="moderate"){
  risk_left1<-Af$risk_mleft
  risk_right1<-Af$risk_mright

  risk_left2<-Al$risk_mleft
  risk_right2<-Al$risk_mright
}

plot(Af$d,risk_left1,xlim=range(Af$d),ylim=c(0,1),type="b",col="red",
     xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
lines(Af$d,risk_right1,type="b",col="blue")

@@

plot(Al$d,risk_left2,xlim=range(Al$d),ylim=c(0,1),type="b",col="red",
     xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
lines(Al$d,risk_right2,type="b",col="blue")
mtext(paste0("r = ", round(rlist[lasta],5)))

@@

#------------- for extreme tail dep. noise : local dispersal ---------------------
pdf("./Results/allmodel_ext_risk_local_disp_extremenoise.pdf",height=12,width=9)

@@

#------------- for moderate tail dep. noise : local dispersal ---------------------
pdf("./Results/allmodel_ext_risk_local_disp_moderatenoise.pdf",height=12,width=9)

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend(x=0.7,y=1.05, c("noise : LTdep.","noise : RTdep."), lty=c(1,1), pch=c(1,1), 
       col=c('red', 'blue'), horiz=F, bty='o', cex=1.5, adj=0)
mtext(paste("Ricker model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
#mtext(paste("(K = 50, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist,noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Hassell model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 100, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_hassell_local
rlist<-hassell_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Maynard Smith model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 4, ", sigma,"=0.8 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_msmith_local
rlist<-msmith_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Pennycuick model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.1, b = 0.1, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_pennycuick_local
rlist<-pennycuick_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 1, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_verhulst_local
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Austin-Brewer model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( s = 0.2, K = 50, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_abrewer_local
rlist<-abrewer_extrisk_d0$r
getplot(x=x,rlist = rlist,noisetype = "moderate")
